---
title: "NEWS-MBSS_TaxaMaster"
output: github_document
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

MBSStools_SuportFiles v0.1.0.9008 (2020-05-21)
================
* ReadMe
    + Modify R code example to get CSV file as well as XLS.


MBSStools_SuportFiles v0.1.0.9007 (2020-05-21)
================
* Data
    + Added CSV file versions of each master taxa list.

MBSStools_SuportFiles v0.1.0.9006 (2020-05-18)
================
* ReadMe
    + Added Updates section.
    
MBSStools_SuportFiles v0.1.0.9005 (2020-05-01)
================
* ReadMe
    + Update GIS file link.

MBSStools_SuportFiles v0.1.0.9005 (2020-04-30)
================
* Update GIS files, Issue #3.
* ReadMe
    + Edit for new files.
    + Update example code.

MBSStools_SuportFiles v0.1.0.9004 (2020-04-30)
================
* Add GIS files.  Issue #3.

MBSStools_SuportFiles v0.1.0.9003 (2020-04-30)
================
* Rename to MBSStools_SupportFiles
* ReadMe
    + Edit for name change.
    + Add section about GIS files.  Issue #3.

MBSS_MasterTaxa v0.1.0.9002 (2020-01-21)
================
* Update badge URL.

MBSS_MasterTaxa v0.1.0.9001 (2020-01-21)
================
* Update file names, Issue #1.
* Update ReadMe with instructions for accessing the files from within R.
* Add NEWS file and update it.

MBSS_MasterTaxa v0.1.0 (2020-01-20)
================
* Initial commit.
* Added master taxa list files.

